Noisy Learning

### 2023-11-23 Model/_learning_noise.qmd
misc

```{r}
library(abc)
library(mvtnorm)
fit_alm_sim <- function(data, c, lr, noise_sd, inNodes, outNodes) {
  train_data <- data[, c("trial", "input", "cor")] %>% rename("vx" = cor)

>>>>

```r
library(abc)
library(mvtnorm)
fit_alm_sim <- function(data, c, lr, noise_sd, inNodes, outNodes) {
  train_data <- data[, c("trial", "input", "cor")] %>% rename("vx" = cor)
